### 2015-07-24 doc/thesis/system.tex
Fixing rules to use the new syntactic categories

Well-formed table types also do not allow \emph{unique} and
\emph{open} table types to appear in the type of the values.
We made this restriction because our type system does not keep
track of aliases to table fields.
This means that allowing \emph{unique} and \emph{open} table
types to appear in the type of a value would allow the
creation of unsafe aliases.
Due to this restriction, the rule that type check table fields
use the auxiliary function \emph{fix} (in the definition of \emph{vt})
to change any \emph{unique} and \emph{open} table types
used in the field initializer to \emph{fixed}.
Rule \textsc{T-FIELD} defines this behavior:
\[
\begin{array}{c}
\mylabel{T-FIELD}\\
\dfrac{\env_{1}, \penv \vdash e_{2}:V, \env_{2} \;\;\;
       \env_{2}, \penv \vdash e_{1}:F, \env_{3}}
      {\env_{1}, \penv \vdash [e_{1}] = e_{2}: (F,vt(V)), \env_{3}}
\end{array}
\]

@@

The rule \textsc{T-CONSTRUCTOR2} uses these steps to type check a
table constructor with a list of table fields that do not end with
an expression that potentially returns multiple values:
\[
\begin{array}{c}
\mylabel{T-CONSTRUCTOR2}\\
\dfrac{\begin{array}{c}
       \env_{1}, \penv \vdash ([e_{1}] = e_{2})_{i}:(F_{i},V_{i}), \env_{i+1} \\
       T = \{F_{1}{:}V_{1}, ..., F_{n}{:}V_{n}\}_{unique} \;\;\;
       wf(T) \;\;\;
       n = |\;\overline{[e_{1}] = e_{2}}\;| \\
       \env_{f} = merge(\env_{1}, ..., \env_{n+1})
       \end{array}}
      {\env_{1}, \penv \vdash \{\;\overline{[e_{1}] = e_{2}}\;\}:T, \env_{f}}
\end{array}
\]

Back to our example, the constructor
$\{ [1] = ``x", [2] = ``y", [3] = ``z" \}$ has type
$\{1:``x", 2:``y", 3:``z"\}_{unique}$ through rule \textsc{T-CONSTRUCTOR2}.
The subtyping rule for \emph{unique} table types allows us assigning
this table to a variable with a more general type such as
$\{1:\String, 2:\String, 3:\String\}_{closed}$ or even
$\{\Integer:\String \cup \Nil\}_{closed}$.

As another example, the constructor $\{[``x"] = 1, [``y"] = \{[``z"] = 2\}\}$
has type $\{``x":1, ``y":\{``z":2\}_{fixed}\}_{unique}$ through rule
\textsc{T-CONSTRUCTOR2}.
The inner table is \emph{fixed} to prevent the creation of unsafe aliases.

@@

We do not need to close \emph{unique} and \emph{open} tables that
appear in the left-hand side of assignments, because \textsc{T-IDREAD}
is sufficient to forbid the creation of an alias to another \emph{unique}
or \emph{open} table.
For this reason, identifiers that appear in the left-hand side
of assignements have their own rule \textsc{T-IDWRITE}:
\[
\begin{array}{c}
\mylabel{T-IDWRITE}\\
\dfrac{\env_{1}(id) = F}
      {\env_{1}, \penv \vdash id_{l}:F, \env_{1}}
\end{array}
\]

>>>>

Well-formed table types also do not allow \emph{unique} and
\emph{open} table types to appear in the type of the values.
We made this restriction because our type system does not keep
track of aliases to table fields.
This means that allowing \emph{unique} and \emph{open} table
types to appear in the type of a value would allow the
creation of unsafe aliases.
Due to this restriction, the rule that type check table fields
use the auxiliary function \emph{fix} (in the definition of \emph{vt})
to change any \emph{unique} and \emph{open} table types
used in the field initializer to \emph{fixed}.
Rule \textsc{T-FIELD} defines this behavior:
\[
\begin{array}{c}
\mylabel{T-FIELD}\\
\dfrac{\env_{1}, \penv \vdash e_{2}:V, \env_{2} \;\;\;
       \env_{2}, \penv \vdash e_{1}:F, \env_{3}}
      {\env_{1}, \penv \vdash [e_{1}] = e_{2}: (F,vt(F,V)), \env_{3}}
\end{array}
\]

@@

The rule \textsc{T-CONSTRUCTOR1} uses these steps to type check a
table constructor with a list of table fields that do not end with
an expression that potentially returns multiple values:
\[
\begin{array}{c}
\mylabel{T-CONSTRUCTOR1}\\
\dfrac{\begin{array}{c}
       \env_{1}, \penv \vdash ([e_{1}] = e_{2})_{i}:(F_{i},V_{i}), \env_{i+1} \\
       T = \{F_{1}{:}V_{1}, ..., F_{n}{:}V_{n}\}_{unique} \;\;\;
       wf(T) \;\;\;
       n = |\;\overline{[e_{1}] = e_{2}}\;| \\
       \env_{f} = merge(\env_{1}, ..., \env_{n+1})
       \end{array}}
      {\env_{1}, \penv \vdash \{\;\overline{[e_{1}] = e_{2}}\;\}:T, \env_{f}}
\end{array}
\]

Back to our example, the constructor
$\{ [1] = ``x", [2] = ``y", [3] = ``z" \}$ has type
$\{1:``x", 2:``y", 3:``z"\}_{unique}$ through rule \textsc{T-CONSTRUCTOR1}.
The subtyping rule for \emph{unique} table types allows us assigning
this table to a variable with a more general type such as
$\{1:\String, 2:\String, 3:\String\}_{closed}$ or even
$\{\Integer:\String \cup \Nil\}_{closed}$.

As another example, the constructor $\{[``x"] = 1, [``y"] = \{[``z"] = 2\}\}$
has type $\{``x":1, ``y":\{``z":2\}_{fixed}\}_{unique}$ through rule
\textsc{T-CONSTRUCTOR1}.
The inner table is \emph{fixed} to prevent the creation of unsafe aliases.

@@

We do not need to close \emph{unique} and \emph{open} tables that
appear in the left-hand side of assignments, because \textsc{T-IDREAD}
is sufficient to forbid the creation of an alias to another \emph{unique}
or \emph{open} table.
For this reason, identifiers that appear in the left-hand side
of assignements have their own rule \textsc{T-IDWRITE1}:
\[
\begin{array}{c}
\mylabel{T-IDWRITE1}\\
\dfrac{\env_{1}(id) = F}
      {\env_{1}, \penv \vdash id_{l}:F, \env_{1}}
\end{array}
\]
